Analytical Predictions of Explanet Obliquities Generated by Planet-Disk Interactions

### 2020-01-22 writeups/Su_disk_disp.tex
stash work

It should be noted that this calculation breaks down in two ways:
\begin{enumerate}
    \item If the evolution of $\hat{s}$ is adiabatic, then it is invalid to
        assume $s_z$ is approximately constant in time, as many
        circulation/libration orbits can ensue. Only when the driving is
        sufficiently impulsive that the evolution dominates the change in $s_z$
        is this calculation valid.

>>>>

We note the resemblance to a similar result given by \citet{malhotra_calc}
describing the impact of a secular resonance sweeping through a system. Both
results have the scaling with repsect to $\epsilon$, despite the vastly
different calculation.

It should be noted that this result breaks down in two ways:
\begin{enumerate}
    \item If the evolution of $\hat{s}$ is adiabatic, then it is invalid to
        assume $s_z$ is approximately constant in time, as many
        circulation/libration orbits can ensue. Only when the driving is
        sufficiently impulsive that the evolution dominates the change in $s_z$
        is this calculation valid.
